\documentclass[preprint, 3p,
authoryear]{elsarticle} %review=doublespace preprint=single 5p=2 column
%%% Begin My package additions %%%%%%%%%%%%%%%%%%%

\usepackage[hyphens]{url}

  \journal{Ecological Letters} % Sets Journal name

\usepackage{lineno} % add
  \linenumbers % turns line numbering on

\usepackage{graphicx}
%%%%%%%%%%%%%%%% end my additions to header

\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \usepackage{fontspec}
  \ifxetex
    \usepackage{xltxtra,xunicode}
  \fi
  \defaultfontfeatures{Mapping=tex-text,Scale=MatchLowercase}
  \newcommand{\euro}{€}
\fi
% use microtype if available
\IfFileExists{microtype.sty}{\usepackage{microtype}}{}
\usepackage[]{natbib}
\bibliographystyle{plainnat}

\ifxetex
  \usepackage[setpagesize=false, % page size defined by xetex
              unicode=false, % unicode breaks when used with xetex
              xetex]{hyperref}
\else
  \usepackage[unicode=true]{hyperref}
\fi
\hypersetup{breaklinks=true,
            bookmarks=true,
            pdfauthor={},
            pdftitle={Does detection distance vary by source? Comparing results from recorded bird song vs.~natural bird song.},
            colorlinks=false,
            urlcolor=blue,
            linkcolor=magenta,
            pdfborder={0 0 0}}

\setcounter{secnumdepth}{5}
% Pandoc toggle for numbering sections (defaults to be off)


% tightlist command for lists without linebreak
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}



\usepackage{float}



\begin{document}


\begin{frontmatter}

  \title{Does detection distance vary by source? Comparing results from
recorded bird song vs.~natural bird song.}
    \author[University of British Columbia]{Ryan Gill%
  \corref{cor1}%
  \fnref{1}}
   \ead{rygill@gmail.com} 
    \author[Another University]{Chas McMurtry%
  %
  }
  
      \affiliation[Technology]{Department, Street, City, State, Zip}
    \affiliation[Another University]{Department, Street, City, State,
Zip}
    \cortext[cor1]{Corresponding author}
  
  \begin{abstract}
  Birds sing in different ways. Some birds are loud, others are quiet.
  Birds sound better in nature than in a recording.
  \end{abstract}
    \begin{keyword}
    ecology \sep 
    birds
  \end{keyword}
  
 \end{frontmatter}

\hypertarget{introduction}{%
\section{Introduction}\label{introduction}}

\emph{Birds are loud} {[}@``bchydro''2008{]}

\hypertarget{methods}{%
\section{Methods}\label{methods}}

Some birds sang, others were in cages.

\hypertarget{results}{%
\section{Results}\label{results}}

Figure \ref{fig1} is generated using an R chunk.

\hypertarget{discussion}{%
\section{Discussion}\label{discussion}}

Birds birds birds\citep{2007for2008}.

\renewcommand\refname{References}
\bibliography{mybibfile.bib}


\end{document}
